Dirace: Practical Proof Automation of Dirac Notation Equations

### 2025-01-23 labelled.tex
2025/1/23

These rules are added to the rewriting system in ~\Cref{sec: decide} and executed together.
In the end, if there are no variables of $\DType(s_1, s_2)$, the expression will be reduced to the addition of big operator sum, and each sum body is Dirac notation scalar with labelled basis.

\begin{lemma}
    For a well-typed term $e$ in $E[\Gamma]$, if $e$ does not contain variables of $\DType(s_1, s_2)$ type, the normal form of $e$ will be
    \[
    \sum_{i}\cdots\sum_{j} a_1 . (\ket{i}_{p} \otimes \cdots \otimes \bra{j}_{q})
    + \cdots +
    \sum_{k}\cdots\sum_{l} a_m . (\ket{k}_{r} \otimes \cdots \otimes \bra{l}_{s})
    \]
    Where $a_i$ are scalar typed Dirac notations.
\end{lemma}

>>>>

These rules are added to the rewriting system in~\Cref{sec: decide} and executed together.
In the end, if there are no variables of $\DType(s_1, s_2)$, the expression will be reduced to the addition of big operator sum, and each sum body is Dirac notation scalar with labelled basis.

\begin{lemma}[normal form]
    \label{lem: labelled normal form}
    For a well-typed term $e$ in $E[\Gamma]$, if $e$ does not contain variables of $\DType(s_1, s_2)$ type, the normal form of $e$ will be
    \[
    \sum_{i}\cdots\sum_{j} a_1 . (\ket{i}_{p} \otimes \cdots \otimes \bra{j}_{q})
    + \cdots +
    \sum_{k}\cdots\sum_{l} a_m . (\ket{k}_{r} \otimes \cdots \otimes \bra{l}_{s})
    \]
    Where $a_i$ are scalar typed Dirac notations.
\end{lemma}
